Identification and Spatial Analysis of Law Firms Naming Patterns in Russia Using Text Embeddings

### 2025-01-28 law-firms-names/Paper.Rmd
Edit introduction and some parts of methods, #4

**Keywords:** firm names; law firms; text embeddings; economic regions, text similarity; large language models.

@@

Law firm names may follow a number of patterns. A pattern can be defined as as a typical model, or pattern, of brand construction identified by usage of identical or semantically similar words or phrases. For example, names with the words “law firm” or “law company” follow one pattern, and names with the words “legal aid” are an example of another pattern. Patterns may be grouped multiple times forming a tree-like classification [@Anora2015]. Such classification may become a basis for identifying naming strategies. Compared to naming patterns, naming strategies are broader groups of firm names that are usually based on sharing a common purpose — e.g. emphasis the belonging of a company to a certain activity type. @BassolsiGardella2023 argue for a two-dimensional Strategic Naming Model (SNM) that includes two pairs of strategies: belonging and uniqueness, no-strategy and market. Pairs may be represented as X and Y axes of a plot, respectively, with paired strategies taking opposite positions on these axes: belonging is an opponent of uniqueness, market is an opponent for no-strategy. Authors of the aforementioned paper discover a difference in naming strategies composition of tourist industry firms in three Columbia cities. Probably such a variation is not be limited to Columbia cities and tourism and can be found in the case with law firms in Russia.

The aim of this research is twofold. First, it tries to identify law firms naming patterns in Russia and categorize them following the framework of SNM. Second, it seeks to check whether there are regularities in the spatial distribution of law firms naming patterns. The potential viability of these two statements cannot be directly conducted from the existing research, but it relies on a common-sense observations about the similarities and differences of law firm names in and between various regions of the country. According to the famous Tobler's First Law of Geography, “near things are more related than distant things” [@Tobler1970], so there is a chance that law firms naming patterns may form spatial clusters and hotspots that at least a bit reflect some economic and, to a lesser extent, cultural similarities of the territories where these firms are located. Given the vast area and a material heterogeneity of economical and cultural landscape of Russia, these names should not have a uniform spatial distribution. However, it is just a hypothesis that needs testing.

@@

## 2.1. Data

@@

To address these challenges, a unified state registry of small and medium-sized enterprises (SME registry) may be used [@SMERegistry2024]. The registry has been maintained since 2016 in accordance with Article 4.1 of the Federal Law of 24 July 2007 No. 209-FZ “On the development of small and medium-sized businesses in the Russian Federation”. As a rule of thumb, all companies and individual entrepreneurs with a yearly revenue below 2 billion roubles and an average yearly number of employees below 250 are automatically included in the SMB registry, without any action being required on their part. There are additional qualifications for the SME registry, e. g. absence of non-SME or foreign control such as, but these should not affect a material portion of law firms. The registry is fully downloadable at the FTS open data portal at no cost. Additionally, the portal provides a monthly record of updates made since the registry's inception. To sum it up, the SMB registry can be regarded as the most comprehensive free data source offering information on Russian business entities, both organizations and individuals.

The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds compatible with NACE Rev.2. It should be noted that the registry does not include several types of firms, e.g. foreign commercial law firms without a juridical person registered according to Russian law, non-profit organizations, bar (advocacy) establishments, large companies etc. This results in some data being absent. Nevertheless, this issue should be considered insignificant for a variety of reasons. Foreign law firms usually register their affiliated juridical person in Russia and thus are not omitted in the registry. Non-profit organisations' share on Russian legal market does not exceed 1% [@Moiseeva2016]. The names of bar establishments are usually quite uniform, containing the kind of the establishment (cabinet of an advocate, bureau of advocates, college of advocates, juridical consultancy) accompanied with a personal name(s) of advocates or with a mention of geographical location of a particular establishment, thus their potential spatial heterogeneity is not characteristic. A matching of the list of the law firms obtained from the SME registry and active in 2023 with the extract of law firms from the Russian Financial Statements Database for the same year shows that ~3,300 of the firms present in SME registry are absent from RFSD, and ~5,200 firms present in RFSD are missing in SME registry. The balance of missing records is not that far from the equality, and with the total number of law firms in SME registry (~34000) the share of missing entries is below 15%. Consequently, the completeness of information is relatively high, and it can be used to draw reliable conclusions.

@@

In this study, the term “law firm” is defined as a commercial organization registered in Russia in accordance with the Civil Code of Russia, with a NACE Rev.2-compatible main activity code equal to 69.10 (activity in the area of law). The aforementioned definition excludes individual entrepreneurs, foreign companies, non-profit organizations, advocacy firms, and notaries. The selection technique based on the main activity code is derived from that proposed by @Moiseeva2016. Individual entrepreneurs are excluded from the analysis because they typically operate under their personal names, and even if they have a brand, it is not listed in the SME registry. Other types of law firms are not included in the analysis primarily due to data availability issues.

The data used in the study covers a period of six years, from 2016 to 2021. The initial point in time is defined by the commencement of SME registry data availability. The finish point, 2021, is the latest year, is the latest year with “normal” conditions in Russia not impacted by military operation in Ukraine and consequent international sanctions and domestic economic and political perturbations. The purpose of temporal dimension is to exclude short-living law firms that are likely to be dummy companies. Organizations with a lifespan of less than three years have been omitted from the research, while all the remaining have been included in the further analysis. In addition, the utilization of multi-year data acts as a form of averaging, smoothing the potential distortions of spatial structure resulting from the random year-to-year changes of active law firms list.

@@

The Yandex Foundation Models cloud service [@Yandex2024] is used to transform the firm names into text vectors, or embeddings. The “text-search-query” model is selected because its purpose, as stated in the documentation, is to vectorize short texts. Prior to vectorization, the firm names are preprocessed to remove indications of organizational form such as “limited liability company”. This is done because such indications are common to the majority of names and thus have little value. The results of the queries to the Yandex API are stored separately for reuse, given that API calls are paid and take time to be completed. The dimension of a firm name vector is 256. Contextual embeddings (YandexGPT) were used in favor of static ones (e.g. FastText), because during the preliminary analysis, they have resulted in far better clusterisation of law firm names (see the description of this step below) which is crucial for naming strategies identification.

### 2.2.4. Naming strategies identification

The dimension of law firm names vectors is reduced from 256 to 2 with the UMAP method, and the resulting 2D vectors are clustered using the DBSCAN technique and plotted to illustrate the results. The clusters are subsequently subjected to manual analysis. A random sample of 20 names is selected from each cluster. The names samples are carefully examined, and each cluster is attached a concise description (e.g. “Consulting companies”), a category, and a strategy. Clusters with descriptions, categories and strategies form a tree-like hierarchy where clusters make up categories, and categories belong to strategies.

The concept of naming strategies is derived from the works of @Arora2015 and @BassolsiGardella2023. The latter paper proposes a strategic naming model with four broad naming strategies, namely “Uniqueness”, “Belonging”, “Market”, and “No-strategy”. Thee strategies form a 2×2 matrix, where two pairs of “Uniqueness vs Belonging” and “Market vs No-strategy” are axes, and strategies in the pairs are opposite to each other. Though invented for classification of names of companies in tourism, this naming framework fits well for the purpose of law firm names grouping. The specific descriptions and their mapping to the categories and strategies are provided, explained and analysed in the results section below.

@@

There are `r initial_firms_count` law firms in the SMB registry in the selected period with `r nrow(unique_names)` unique firm names. From the initial dataset, `r valid_firms_count` law firms have existed for at least three years and have been selected for the analysis. Their names sometimes are duplicated, and the number of unique law firm names being analysed is `r`.

>>>>

**Keywords:** firm names; law firms; text embeddings; spatial analysis, autocorrelation, naming strategies.

@@

Law firm names can follow different patterns. A naming pattern can be defined as as a typical way of branding, identified by the use of identical or semantically similar words or phrases. For instance, the names “Law firm “Femida” and “Law company “Alibi” follow one pattern, while “Centre of legal aid and support” is an example of another. Patterns can be grouped several times to form a hierarchical classification [@Anora2015]. Such a classification can help to identify naming strategies. Compared to patterns, strategies are broader groups of names, usually based on a common purpose, e.g. highlighting a company's affiliation to a certain activity (retail, banking, transport, education, etc). @BassolsiGardella2023 propose a two-dimensional Strategic Naming Model (SNM) that includes two pairs of opposing strategies: belonging and uniqueness, no-strategy and market. They discover a difference between three Colombian cities in the naming strategies of their tourism companies. It is likely that such a variation is not be limited to the cities of Colombia and the tourism industry and can also be found in the case of law firms in Russia.

The aim of this research is twofold. First, it attempts to identify the naming patterns of law firms in Russia and to categorise them according to the SNM framework. Second, it seeks to test whether there are any regularities in the spatial distribution of these patterns. The potential viability of these two propositions cannot be derived directly from the existing research, but is based on common sense observations of the similarities and differences of law firm naming in and between different regions of the country. It is highly unlikely that the names of law firms in Russia are so diverse as to be impossible to classify. Their geographical distribution is a much more difficult issue. At first glance, there are no obvious factors that could lead lawyers in a particular region to choose a common naming pattern for their firms. However, according to the famous Tobler's First Law of Geography, “near things are more related than distant things” [@Tobler1970], there is a possibility that law firm naming patterns may form spatial clusters and hotspots that reflect, at least to some extent, economic and cultural similarities of the territories in which these firms are located. There is an evidence of regional variation of branding in food industry [@Goroshko2022] and wine production [@Klimenko2023] in Russia. Even though the market of legal services seems to be far less dependant on the properties of place, the question of spatial regularities in naming patterns is also intriguing and worth testing.

@@

## 2.1. Background

## 2.2. Data

@@

To address these challenges, a unified state registry of small and medium-sized enterprises (SME registry) may be used [@SMERegistry2024]. The registry has been maintained since 2016 in accordance with Article 4.1 of the Federal Law of 24 July 2007 No. 209-FZ “On the development of small and medium-sized businesses in the Russian Federation”. As a rule of thumb, all companies and individual entrepreneurs with a yearly revenue below 2 billion roubles and an average yearly number of employees below 250 are automatically included in the SME registry, without any action being required on their part. There are additional qualifications for the SME registry, such as the absence of non-SME or foreign control, but these are unlikely to affect a significant proportion of law firms. The registry is fully downloadable at the FTS open data portal at no cost. Additionally, the portal provides a monthly record of updates made since the registry's inception. To sum it up, the SMB registry can be regarded as the most comprehensive free data source offering information on Russian business entities, both organisations and individuals.

The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds compatible with NACE Rev. 2 (European Classification of Economic Activities). It should be noted that the registry does not include several types of firms such as foreign commercial law firms without a juridical person registered under Russian law, non-profit organisations, bar (advocacy) formations, large enterprises. As a result, some data are missing. However, for a number of reasons, this problem should be considered insignificant. Foreign law firms usually register their affiliated juridical person in Russia and are therefore not omitted from the SME registry. The share of non-profit organisations in the Russian legal services market does not exceed 2% [@Moiseeva2016]. The names of bar (advocacy) formations are usually quite uniform. They contain the kind of the formation (advocate's office, advocate's bureau, college of advocates, juridical consultancy) accompanied by the personal name(s) of advocates or a reference to a geographical location. Their naming patterns are thus quite apparent and do not require further investigation. Large enterprises represent only a tiny minority of law firms.

For a validation, a list of law firms' unique tax IDs obtained from the SME registry for the year 2023 is matched with the list of law firms' tax IDs from the Russian Financial Statements Database (RFSD) [@Bondarkov2025] for the same year. The comparison shows that ~3,300 of the firms present in the SME registry are missing from the RFSD, and ~5,200 firms present in the RFSD are missing from the SME registry. The balance of missing records is not so far from being equal. The SME registry contains ~34000 law firms for the year 2023, so the missing rate is below 15%. Consequently, the completeness of the data is relatively high and reliable conclusions can be drawn.

@@

In this study, the term “law firm” is defined as a commercial organization registered in Russia in accordance with the Civil Code of Russia, with a NACE Rev. 2-compatible main activity code equal to 69.10 (activity in the area of law). The aforementioned definition excludes individual entrepreneurs, foreign companies, non-profit organizations, bar (advocacy) formations, and notaries. The selection technique based on the main activity code is derived from that proposed by @Moiseeva2016. Individual entrepreneurs are excluded from the analysis because they typically operate under their personal names, and even if they have a brand, it is not listed in the SME registry. Other types of law firms are not included in the analysis primarily due to data availability issues.

The data used in the study cover a period of six years, from 2016 to 2021. The initial point in time is defined by the commencement of SME registry data availability. The end point, 2021, is the last year of “normal” conditions in Russia unaffected by the military operation in Ukraine and the resulting international sanctions and domestic economic and political turmoil. The purpose of the time dimension is to rule out short-lived law firms, which are likely to be shell companies. Organisations with a lifespan of less than three years are excluded from the research, while all the remaining are included in the further analysis. In addition, the use of multi-year data acts as a form of averaging, smoothing out the potential biases in the spatial structure caused by random annual changes in the population of active law firms.

@@

The Yandex Foundation Models cloud service [@Yandex2024] is used to transform the firm names into text vectors, or embeddings. The “text-search-query” model is selected because its purpose, as stated in the documentation, is to vectorize short texts. Prior to vectorization, the firm names are preprocessed to remove indications of organizational form such as “limited liability company”. This is done because such indications are common to the majority of names and thus have little value. The results of the queries to the Yandex API are stored separately for reuse, given that API calls are paid and take time to be completed. The dimension of a firm name vector is 256. Contextual embeddings (YandexGPT) were used in preference to static ones (e.g. FastText), because in the preliminary analysis, they have resulted in a much better clustering of law firm names, which is crucial for naming patterns identification.

### 2.2.4. Naming patterns identification and classification

Law firm names are clustered using the KMeans technique. A matrix of features for clustering is constructed from the name embeddings. As there are 256 elements in each vector, the feature matrix has 256 columns. A target number of clusters is determined with the elbow method and ultimately set to 50, with the understanding that further manual processing of the clustering results will be necessary. Each name is assigned a cluster label between 1 and 50. Despite the simplicity of the clustering algorithm, which can even be considered old-fashioned compared to (H)DBSCAN, it performs quite well on the data at hand. Preliminary tests have shown that the clusters identified by (H)DBSCAN are not significantly better than those obtained by KMeans, but the latter takes much less times and memory. It is important to emphasise that automatic clustering is only a auxiliary step in the identification and classification of naming strategies which aims to facilitate the manual data processing by breaking down the entire set of law firm names into the compact groups that can be analysed more easily by a human. Therefore, there is no reason to improve the quality of clustering too much.

The resulting clusters are then manually grouped. A random sample of 20 names is selected from each cluster. With 50 clusters and 20 sampled names allocated in each, the total size of the dataset for manual processing is 1, 000. The cluster samples are carefully examined, and a concise description is provided for each, e.g. “Names with the word “консалт/консалтинг” (consult/consulting)”. After this, the clusters are examined again and assigned to a naming pattern, e.g. “Consulting” or “Law firm”. Finally, the clusters and their naming patterns are divided into four previously mentioned naming strategies derived from @BassolsiGardella2023. Each cluster belongs to a single pattern, and each pattern belongs to a single strategy. Each strategy consists of several patterns, and each pattern consists of one or many clusters, forming a hierarchical structure.

Each group except for the “Misc” category represents a specific naming strategy. The “Form” strategy encompasses names that are based on a word or words denoting a kind of business entity, including “company”, “firm”, “group”, “partnership”, “center”, “alliance”, and “corporation”. The “Law” strategy emphasizes the firm's affiliation with the legal services market, employing terms such as “legal”, “juridical”, “lex”, “law”, and “lawyer”. Names belonging to the “Service” strategy may indicate a particular service provided by a law firm (“advisor”, “consulting”, “protection”, “support”, “warrant”), describe the sectors of businesses the firm is primarily engaged with (“technology”, “development”, “house management”, “accounting”), or mention services in general. The “Misc” category is a catch-all group for names that do not clearly align with any other category.

@@

There are `r initial_firms_count` law firms in the SME registry in the selected period with `r nrow(unique_names)` unique names. From the initial dataset, `r valid_firms_count` law firms have existed for at least three years and have been selected for the analysis. Their names are sometimes duplicated, and the number of unique law firm names being analysed is `r length(unique(clustered$name))`.
